Disk Heating, Galactoseismology, and the Formation of Stellar Halos

### 2017-06-27 paper/paper.tex
abstract

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{
%A single paragraph of about 200 words maximum. 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
Deep photometric surveys of the Milky Way have revealed diffuse structures
encircling our Galaxy in regions far beyond the ``classical'' end of the
stellar disk.
This article reviews results from our own and other observational programs, which together suggest that, despite their extreme positions, the stars in these structures were nevertheless formed in our Galactic disk.
Mounting evidence from recent observations and simulations implies kinematic connections between several of these distinct structures.
This suggests the existence of collective disk oscillations that can plausibly be traced all the way to asymmetries seen in the stellar velocity distribution around the Sun.
There are multiple interesting implications of these findings:
they promise new perspectives on the process of disk heating;
they provide direct evidence for a stellar halo formation mechanism in addition to the accretion and disruption of satellite galaxies; and,
they motivate searches of current and near-future surveys to trace these oscillations across the Galaxy.
Such maps could be used as dynamical diagnostics in the emerging field of ``Galactoseismology,'' which promises to model the history of interactions between the Milky Way and its entourage of satellites, as well examine the density of our dark matter halo.
As sensitivity to very low surface brightness features around external galaxies increases, many more examples of such disk oscillations will likely be identified.
Statistical samples of such features not only encode detailed information about
interaction rates and mergers, but also about long sought-after dark matter
halo densities and shapes.
Models for the Milky Way's own Galactoseismic history will therefore serve as a
critical foundation for studying the weak interactions of galaxies across the
universe.
}

>>>>

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{
%A single paragraph of about 200 words maximum. 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.
Deep photometric surveys of the Milky Way have revealed diffuse structures
encircling our Galaxy far beyond the ``classical'' end of the stellar disk.
This article reviews results from our own and other observational programs, which together suggest that, despite their extreme positions, the stars in these structures were formed in our Galactic disk.
Mounting evidence from recent observations and simulations implies kinematic connections between several of these distinct structures.
This suggests the existence of collective disk oscillations that can plausibly be traced all the way to asymmetries seen in the stellar velocity distribution around the Sun.
There are multiple interesting implications of these findings:
they promise new perspectives on the process of disk heating;
they provide direct evidence for a stellar halo formation mechanism in addition to the accretion and disruption of satellite galaxies; and,
they motivate searches of current and near-future surveys to trace these oscillations across the Galaxy.
Such maps could be used as dynamical diagnostics in the emerging field of ``Galactoseismology,'' which promises to model the history of interactions between the Milky Way and its entourage of satellites, as well examine the density of our dark matter halo.
As sensitivity to very low surface brightness features around external galaxies increases, many more examples of such disk oscillations will likely be identified.
Statistical samples of such features not only encode detailed information about
interaction rates and mergers, but also about long sought-after dark matter
halo densities and shapes.
Models for the Milky Way's own Galactoseismic history will therefore serve as a
critical foundation for studying the weak interactions of galaxies across the
universe.
}
